openarchaeoCollaboration

### 2022-04-25 analysis/paper.Rmd
Comment on GitHub hegemony

## Background
- The notion of the archaeological toolbox, and its inclusion of digital tools and skillsets
  - The use of off-the-shelf tools like MS Access, Excel, Agisoft PhotoScan, Dropbox, etc
  - Link to related factors:
    - Lack of experienced programmers among archaeologists
    - The built-in flexibility of these tools
    - Ease of administrative purchasing through university departments
  - What changed?
    - Software is expensive, shift to subscription models, locking into a dependency on a commercial service provider
    - Archaeologists are better at computer programming, digital literacy on the rise, digital archaeologists grows into its own legitimate sub-discipline
    - Open source is cool, everyone has a github profile (even if not really)

>>>>

## Background
- The notion of the archaeological toolbox, and its inclusion of digital tools and skillsets
  - The use of off-the-shelf tools like MS Access, Excel, Agisoft PhotoScan, Dropbox, etc
  - Link to related factors:
    - Lack of experienced programmers among archaeologists
    - The built-in flexibility of these tools
    - Ease of administrative purchasing through university departments
  - What changed?
    - Software is expensive, shift to subscription models, locking into a dependency on a commercial service provider
    - Archaeologists are better at computer programming, digital literacy on the rise, digital archaeologists grows into its own legitimate sub-discipline
    - Open source is cool, everyone has a github profile (even if not really)
      - (JR:) People are presumably guided towards GitHub (or at least git) via other routes, because it's seen as the standard platform for 'open' digital work. For example, the literature on reproducible compendiums recommends GitHub, and almost all R development work is now done there. And once there, you're sort of forced into engaging in a (particular set of) open source development. I know there's controversy about how dominant this has become and people who say it's not 'true' (free and) open source, and perhaps we could add to that the question of whether it's the right model for archaeology.
